Inference for multivariate peaks over threshold models

### 2021-12-01 results.tex
Updates from Overleaf
ccchanges

\begin{figure}[ht]
    \centering
    \caption{Pairwise extremal dependence coefficients for IVT data using the PRG--G model.  
    The left panel corresponds to the ERA-Interim data, the right panel to the ERA5 data.\label{fig:chi_ij}}
    \begin{minipage}{.49\textwidth}
      \centering
      \includegraphics[width=0.99\linewidth]{./images/chi_ij_8}
    \end{minipage}
    \begin{minipage}{.49\textwidth}
      \centering
      \includegraphics[width=0.99\linewidth]{./images/chi_ij_46}
    \end{minipage}
\end{figure}

@@

Figure~\ref{fig:condsurv1d} shows, for the ERA-Interim data under the PRG--G model,  
    the conditional survival curve defined in Equation~\ref{eqn:condsurv}, for one dimension, 
    conditioned on all other dimensions being greater than their (fitted) $90$th percentile. 
    Figure~\ref{fig:condsurv2d} presents the bi-variate conditional survival function,
    conditioning on all other dimensions.  These results illustrate quantitatively how extremal dependence
    affects the shape of the conditional survival curves.  The two top panels represent the joint survival function 
    between grid locations 1 and 2, which are shown in Figure~\ref{fig:chi_ij} to exhibit strong
    extremal dependence.  We observe that the joint survival surface 
    is strongly convex.  The bottom panels represent the joint survival surface between grid locations 2 and 8, 
    which exhibited low extremal dependence.  In this case the shape of the contours tend to be concave, quite different from the shapes observed in the top panels.
% EOF

>>>>

\begin{figure}[ht]
    \centering
    \caption{Pairwise extremal dependence coefficients for IVT data using the PRG--G model.\label{fig:chi_ij}}
    \includegraphics[width=0.9\textwidth]{./images/chi_ij_c}
\end{figure}

@@

Figure~\ref{fig:condsurv1d} shows, for the ERA-Interim data under the PRG--G model,  
    the conditional survival curve defined in Equation~\ref{eqn:condsurv}, for one dimension, 
    conditioned on all other dimensions being greater than their (fitted) $90$th percentile. 
    Figure~\ref{fig:condsurv2d} presents the bi-variate conditional survival function,
    conditioning on all other dimensions.  These results illustrate quantitatively how extremal dependence
    affects the shape of the conditional survival curves.  The two top panels represent the joint survival function 
    between grid locations 4 and 5, which are shown in Figure~\ref{fig:chi_ij} to exhibit strong
    extremal dependence.  We observe that the joint survival surface 
    is strongly convex.  The bottom panels represent the joint survival surface between grid locations 1 and 5, 
    which exhibited low extremal dependence.  In this case the shape of the contours tend to be concave, quite different from the shapes observed in the top panels.
% EOF
